---
title: "Introduction to DukeProteomicsSuite"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DukeProteomicsSuite}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = TRUE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
set.seed(1000)
```

```{r, eval=TRUE, include=TRUE}
library(DukeProteomicsSuite)
```


This vignette introduces DukeProteomicsSuite functions and helps those unfamiliar with energetic proteomics methods to better understand what this package does and how it can be used. We'll start with a rough overview of energetic proteomics methods, then discuss where this package can be used, and finally provide real-world examples. 

# Overview

Proteomics is a broad field of 

Talk about expression level vs phenotype analysis

# OnePotTPP

TPP can be accessed using `OnePotTPP_Phenotype.Fun()` or `OnePotTPP_Ligand.Fun()`
Can introduce error messages if p value is out of range or a TMTPlex is selected which is not currently available
```{r, eval=TRUE, error=TRUE, purl=FALSE}
OnePotTPP_Ligand.Fun(TPPExample_Ligand, p_cutoff = -5)
```
```{r, eval=TRUE, error=TRUE, purl=FALSE}
OnePotTPP_Ligand.Fun(TPPExample_Ligand, TMTplex = 8)
```

Look at example data by `?TPPExample_Ligand`


```{r, eval=FALSE}
OnePotTPP_Phenotype.Fun()
```
Calculates the 
Introduce the method
Go through the analysis
Examples
# OnePotSPROX
Introduce the method
Go through the analysis
Examples
# STEPP/LiP

Here we go `knit`



Here is some code
```{r, eval=FALSE}
library(DukeProteomicsSuite)
```





















































































































































